---
title: "About"
---

About this site

```{r}
1 + 1
```

```{r}
library(tidyverse)
```

Mucho texto

```{r}
a <- 12
if(a == 12){
  print("algoj")
  a <- a - 12
}else{
  warning("hola")
}

```

muchostropeas fjadsfl qweopisadfoipqwe sdaifqweofaslf ajs oiwsalkdf asoidfw qesdaofiqwe sadklfjqwoe dsfasofiqwe oipaofiqw osadf oqwei saoifqwoie usadflj safiweqoutr asdlfjasfoiqweur askljd

<aside>
texto adicional
</aside>

update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text
update text

[This is a span that has the class aside which places it in the margin without a footnote number.]{.aside}

```{r}
#| label: fig-mtcars
#| fig-cap: "MPG vs horsepower, colored by transmission."
#| column: margin

library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')
```
